Consolidating Wind Farm Data in Data Spaces for Training Predictive Maintenance ML

### 2024-06-03 Semantics-2024/paper.qmd
add orcid in paper.qmd

author:
  - name: Robert David
    email: 
    orcid: 
    affiliation: 
     name: The Semantic Web Company
     country: Austria
  - name: Axel Weißenfeld
    email: 
    orcid: 
    affiliation: 
      name: Austrian Institute of Technology
      country: Austria
  - name: Petar Ivanov
    email: 
    orcid: 
  - name: Nikola Tulechki
    email: 
    orcid: 
  - name: Vladimir Alexiev
    email: vladimir.alexiev@ontotext.com
    orcid: 0000-0001-7508-7428
    affiliation: 
      name: Ontotext
      country: Bulgaria
acm-metadata:
  keywords:
    - data spaces
    - oil and gas
    - renewable energy
    - refineries
    - windfarms
    - time series
    - ontologies
    - semantic technologies
  final: true
  # acmart-options: sigconf, review
  # copyright-year: 2024
  # acm-year: 2024
  copyright: acmcopyright
  # doi: 
  # conference-acronym: 
  # conference-name: 
  # conference-date: 
  # conference-location: 
  # isbn:

>>>>

author:
  - name: Robert David
    email: 
    orcid: 
    affiliation: 
     name: The Semantic Web Company
     country: Austria
  - name: Axel Weißenfeld
    email: 
    orcid: 
    affiliation: 
      name: Austrian Institute of Technology
      country: Austria
  - name: Petar Ivanov
    email: petar.ivanov@ontotext.com
    orcid: 0000-0001-8448-1005
  - name: Nikola Tulechki
    email: 
    orcid: 
  - name: Vladimir Alexiev
    email: vladimir.alexiev@ontotext.com
    orcid: 0000-0001-7508-7428
    affiliation: 
      name: Ontotext
      country: Bulgaria
acm-metadata:
  keywords:
    - data spaces
    - oil and gas
    - renewable energy
    - refineries
    - windfarms
    - time series
    - ontologies
    - semantic technologies
  final: true
  # acmart-options: sigconf, review
  # copyright-year: 2024
  # acm-year: 2024
  copyright: acmcopyright
  # doi: 
  # conference-acronym: 
  # conference-name: 
  # conference-date: 
  # conference-location: 
  # isbn:
